Considering scale in multilayer animal social networks

### 2020-06-28 paper/manuscript.Rmd
more conclusion p

<!-- conclusion -->
Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. Recent technological advances in
remotely sensed imagery [@Drusch_2012] and animal tracking devices
[@B_rger_2016; @Wikelski_2007] have increased the availability of complex, high
resolution data. We highlight ways in which scale should be considered when
building social networks from both observed and remotely-sensed data. It is
important to consider a broad continuum of scales to fully capture ecological
processes, carefully select and combine sources of data with different temporal
and spatial scales, and establish a clear link between scales of observation and
meaningful biology.

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology. We demonstrate the novel analyses in varying social, spatial, and
temporal scale within a multilayer framework. We show that (1) multilayer social
networks are scale-dependent, and (2) the use of multilayer networks is useful
for identifying habitat or season-specific social processes. Our multilayer
network analysis of caribou sociality incorporating high resolution GPS
telemetry data and spatial land cover data is grounded in the context of
observed animal behaviour as the scales we chose to explore, e.g., number of
observations and sociality across space and time, are ones that have also
traditionally been done in ethology.
<!-- TODO: round it out -->

>>>>

<!-- conclusion -->
Recognition of scale as a fundamental concept in ecology [@Levin_1992] has lead
to an increased attention to the scale at which ecological processes are
observed [@Schneider_2001; @Chave_2013]. Recent technological advances in
remotely sensed imagery [@Drusch_2012] and animal tracking devices
[@Borger_2020; @B_rger_2016; @Wikelski_2007] have increased the availability of complex, high
resolution data. We highlight ways in which scale should be considered when
building social networks from both observed and remotely-sensed data. Our multilayer
network analysis of caribou sociality incorporating high resolution GPS
telemetry data and spatial land cover data is grounded in the context of
observed animal behaviour as the scales we chose to explore, e.g., number of
observations and sociality across space and time, are ones that have also
traditionally been done in ethology.

Multilayer networks remain a nascent but powerful tool in animal behavioural
ecology and we introduce concepts of scale within the existing multilayer 
framework. Silk et al. (2018) summarized some 
key multilayer questions in animal behaviour
research  and based on our case study of scale in the context of multilayer 
networks, we conclude by posing an additional set of questions on the future 
of multilayer networks through the lens of scale and behavioural, landscape, 
and spatial ecology:

1. How do social phenotypes vary across social, spatial, and temporal scales and
at which scale might these influence fitness? Are some scales better predictors
for different fitness metrics?

2. Why do individuals associate more strongly with certain conspecifics in some
habitats? What, if any, is the role of movement in the context of habitat
networks?

3. How, and why, does the spatial scale of perception influence, e.g. auditory,
visual, or chemotaxis, influence the social environment? What is the role of
memory, and by extension social and spatial cognition, as animals navigate their
environment and make decisions about where to move next?

We show that (1) multilayer social networks are scale-dependent, and (2) the use
of multilayer networks is useful for identifying spatially or temporally
specific social associations. It is important to consider a broad continuum of
scales to fully capture ecological processes, carefully select and combine data
with different temporal and spatial scales, and establish a clear link between
biologically relevant scales of observation.

<!-- TODO: round it out -->
